Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-29 paper/paper-mainfile.tex
update hyptn

% visited checking with task sequences makes totally-ordered visited lists incomplete (with order)

@@

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleCoverage}
	\scalebox{0.8} {
\begin{tabular}{lccccccl} 
	\toprule 
	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO\\  
	\midrule 
	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
			\midrule 
	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
			\midrule 
	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleCoverage}
	\scalebox{0.65} {
		\begin{tabular}{lccccccccccl} 
			\toprule 
			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
			&PO & TO & PO & TO  \\ 
			\midrule 
			Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 0.0 & \textbf{17.0}  \\ 
			Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & 0.0 & \textbf{18.0}   \\ 
			Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}   \\ 
			PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 0.0 & 0.0   \\ 
			Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & 0.0 & 20.0   \\ 
			Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 0.0 & \textbf{25.0}   \\ 
			Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 2.0 & \textbf{35.0}   \\ 
			UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 0.0 & \textbf{21.0}   \\ 
			Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
			\midrule
			Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
			SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 0.0 & 1.0  \\ 
			Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & 0.0 & 5.0  \\ 
			\midrule 
			Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{114.0} & \textbf{268.0}  \\ 
			Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & 1.65 & 8.58  \\ 
			\bottomrule 
		\end{tabular}

@@

\begin{table}
	\centering
	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleIPC}
	\scalebox{0.7} {
\begin{tabular}{lccccccccccl} 
	\toprule 
	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
	&PO & TO & PO & TO  \\  
	\midrule 
	Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & 0.0 & \textbf{0.72}  \\

	Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & 0.0 & 0.54   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & 0.63   \\ 
	PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.0 & 0.0   \\ 
	Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & 0.0 & \textbf{0.97}  \\ 
	Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.0 & \textbf{1.0}   \\ 
	Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.22 & 0.78   \\ 
	UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & 0.0 & 0.92   \\ 
	Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
	\midrule 
	Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.0 & 0.14   \\ 
	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.0 & 1.0   \\ 
	\midrule 
	IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{1.6} & \textbf{7.9}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

>>>>

% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }

@@

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\

\todo{proven unsolvable should not be in superscripts}

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleCoverage}
	\scalebox{0.8} {
\begin{tabular}{lccccccl} 
	\toprule 
	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO\\  
	\midrule 
	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
			\midrule 
	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
			\midrule 
	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleCoverage}
	\scalebox{0.65} {
		\begin{tabular}{lccccccccccl} 
			\toprule 
			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
			&PO & TO & PO & TO  \\ 
\midrule 
Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
\midrule 
Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
\midrule 
Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
\bottomrule 
		\end{tabular}

@@

\begin{table}
	\centering
	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleIPC}
	\scalebox{0.7} {
\begin{tabular}{lccccccccccl} 
	\toprule 
	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
	&PO & TO & PO & TO  \\  
\midrule 
Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
\midrule 
Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
\midrule 
IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
\bottomrule 
\end{tabular} 
	}
\end{table}
